---
title: "ggplot2"
author: "zhiqiang"
date: "2020/7/8"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
```
#cheat sheet summary
1. a <- ggplot(economics, aes(date, unemploy))
2. b <- ggplot(seals, aes(x = long, y = lat)) 
3. c <- ggplot(mpg,aes(hwy))
    +c2 <- ggplot(mpg)
4. d <- ggplot(mpg,aes(fl))
5. e <- ggplot(mpg,aes(cty,hwy))
6. f <- ggplot(mpg,aes(class,hwy))
7. g <- ggplot(diamonds,aes(cut,color))
8. h <- ggplot(diamonds,aes(carat,price))
9. i <- ggplot(economics,aes(date,unemploy))
10. j <- ggplot(df,aes(grp,fit,ymin = fit-se,ymax = fit+se))
11. k <- ggplot(data, aes(fill = murder))
12. l <- ggplot(seals, aes(long, lat))
13. n <- d + geom_bar(aes(fill = fl))
14. o <- c + geom_dotplot(aes(fill = ..x..))
15. p <- e + geom_point(aes(shape = fl, size = cyl))
16. r <- d + geom_bar()
17. s <- ggplot(mpg,aes(fl,fill = drv))
18. t <- ggplot(mpg,aes(cty,hwy))+geom_point()


##load data
```{r, message = F}
#National Parks in California
ca <- read_csv("data/ca.csv") 

#Acadia National Park
acadia <- read_csv("data/acadia.csv")

#Southeast US National Parks
se <- read_csv("data/se.csv")

#2016 Visitation for all Pacific West National Parks
visit_16 <- read_csv("data/visit_16.csv")

#All Nationally designated sites in Massachusetts
mass <- read_csv("data/mass.csv")
```
---

```{r}
head(ca)
```

```{r}
ggplot(data = ca) +
  geom_point(aes(x = year,y = visitors, color =park_name))
```

```{r}
ggplot(data = ca) +
    geom_point(aes(x = year, y = visitors, color = park_name)) +
    labs(x = "Year",
       y = "Visitation",
       title = "California National Park Visitation") +
    theme_dark()
```


```{r}
ggplot(data = se) +
     geom_point(aes(x = year, y = visitors, color = park_name)) +
     facet_wrap(~ state, scales = "free")
```


-----
another way to plot
```{r}
ggplot(data = se) + 
  geom_jitter(aes(x = park_name, y = visitors, color = park_name), 
              width = 0.1, 
              alpha = 0.4) +
  coord_flip() +
  theme(legend.position = "none") 
```

```{r}
ggplot(se, aes(x = park_name, y = visitors)) + 
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
ggplot(se, aes(x = year, y = visitors, color = park_name)) +
   geom_line()
```

##more than one geoms
```{r}
ggplot(data = acadia,aes(x = year, y = visitors)) + 
  geom_point() +
  geom_line(col = "blue") +
  geom_smooth(se = F,col = "red") +
  labs(title = "Acadia National Park Visitation",
       y = "Visitation",
       x = "Year") +
  theme_bw()
```

##geom_bar

```{r}
ggplot(data = visit_16, aes(x = state)) + 
  geom_bar()
```

```{r}
ggplot(data = visit_16, aes(x = state, y = visitors, fill = park_name)) + 
  geom_bar(stat = "identity")
```
```{r}
ggplot(data = visit_16, aes(x = state, y = visitors, fill = park_name)) + 
  geom_bar(stat = "identity", position = "dodge")
```

###the save of the picture.
```{r}
my_plot <- ggplot(data = mass) + 
      geom_bar(aes(x = type, fill = park_name)) +
  labs(x = "", y = "")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7))
ggsave("name_of_file.png", my_plot, width = 15, height = 10)
```


```{r}
pdf('figures/my_plot.pdf')
my_plot <- ggplot(data = mass) + 
      geom_bar(aes(x = type, fill = park_name)) +
  labs(x = "", y = "")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7))
dev.off()
```

